%!TEX root = ../final.tex
\question The \code{food} table contains the latitude and longitude of
restaurants in SF and their food safety rating (0 to 100, higher is better).

\begin{verbatim}
lat       | long        | score
37.791116 | -122.403816 | 98
37.786848 | -122.421547 | 100
37.792888 | -122.403135 | 70
... (6723 rows omitted)
\end{verbatim}

\begin{parts}

\part Sam tried to do some data analysis but didn't get very far. Here are some
variables he defined and how he defined them. The functions
\code{slope(table, x\_label, y\_label)} returns the slope in original units of
the regression line predicting y given x and \code{correlation(table, x\_label,
y\_label)} returns the correlation coefficient $r$ between the variables x and
y.

Write one line of Python code to compute each of the following.
\textbf{In your code, you may only use arithmetic operators, numbers, and the
variables that Sam defined below.}

\begin{verbatim}
name | code
a1   | slope(food, 'lat', 'score')
corr | correlation(food, 'lat', 'score')
m1   | np.mean(food.column('lat'))
m2   | np.mean(food.column('score'))
\end{verbatim}

\begin{subparts}
  \subpart[2] The correlation between score and latitude.

  \begin{verbatim}

____________________________________________________________
  \end{verbatim}

  \begin{solution}
  \begin{verbatim}
corr
  \end{verbatim}
  \end{solution}

  \subpart[3] The prediction for the score given a latitude of 750.

    \begin{verbatim}

____________________________________________________________
    \end{verbatim}

    \begin{solution}
    \begin{verbatim}
a1 * 750 + m2 - a1 * m1
    \end{verbatim}
    \end{solution}

  \subpart[3] The prediction for the latitude given a score of 0. (You don't
  need the next part of this question to solve this one.)

    \begin{verbatim}

____________________________________________________________
    \end{verbatim}

    \begin{solution}
    \begin{verbatim}
m1 - corr * corr / a1 * m2
    \end{verbatim}
    This question was taken out of the exam because you actually did, in fact,
    need part iv to solve this question.
    \end{solution}

  \subpart[3] The slope of the regression line predicting latitude given the
    score in original units.

    \begin{verbatim}

____________________________________________________________
    \end{verbatim}

    \begin{solution}
    \begin{verbatim}
corr * corr / a1
    \end{verbatim}
    \end{solution}
\end{subparts}

\newpage

\part[5] The \code{food} table is repeated here for your convenience.

\begin{verbatim}
lat       | long        | score
37.791116 | -122.403816 | 98
37.786848 | -122.421547 | 100
37.792888 | -122.403135 | 70
... (6723 rows omitted)
\end{verbatim}

Recall that the regression line is the line that minimizes the mean squared
error between the predictions and the actual values. For example, to find the
regression line that uses latitude to predict score we want to choose the slope
and intercept for the line:

\[ \text{predicted score} = slope \cdot lat + intercept \]

So that $ mean((\text{actual score} - \text{predicted score})^2) $ is as small
as possible.

We can use the \code{minimize} function to find this slope and intercept for
us. In particular, in lecture we defined a function
\code{mse(slope, intercept)} that returns the mean squared error given a
choice of slope and intercept. Then, \code{minimize(mse)} returned the slope
and intercept of the regression line.

What if we wanted to use both latitude and longitude to make a prediction? We
can do this by minimizing the mean squared error between the prediction line

\[ \text{predicted score} = slope_1 \cdot lat +
   slope_2 \cdot long + intercept \]

And the actual score. This is
also known by the term \emph{multiple linear regression}.

Fill in the the blanks for \code{multiple\_mse} so that
\code{minimize(multiple\_mse)} will return the three parameters for linear
regression using both latitude and longitude to predict score.

\begin{verbatim}

def multiple_mse(______________________________________________):

    lat = ______________________________________________________

    long = _____________________________________________________

    score = ____________________________________________________

    return np.mean(

    ____________________________________________________________
    )

\end{verbatim}

\begin{solution}
\begin{verbatim}
def multiple_mse(slope1, slope2, intercept):
    lat = food.column('lat')
    long = food.column('long')
    score = food.column('score')

    return np.mean(
      (score - slope1 * lat - slope2 * long - intercept) ** 2
    )
\end{verbatim}
\end{solution}

\end{parts}
