\q{10}{Steph Curry Fan Club}

A group of current Data 8 students who are big fans of Steph Curry are inspired by the current course material to conduct an analysis of Curry's basketball shot record. It turns out Steph Curry has a 58\% chance of successfully shooting the ball in the basket any time he tries. 



\begin{enumerate}
\vskip .2in
\subq{2} Curry shoots the ball twice. What is the probability that both of the shots make it in the basket?\vskip 0.1in
\begin{tabular}{l@{\hskip 1in}l@{\hskip 1in}l@{\hskip 1in}l}
{\bubble} \quad ${\displaystyle \frac{58}{100}\times \frac{58}{99}}$
&\solutionbubble \quad ${\displaystyle 0.58^2}$ \\[10pt]
\bubble \quad ${\displaystyle 2 \times 0.58 }$
&\bubble \quad ${\displaystyle 0.42^2}$

\end{tabular}


\vskip .4in
\subq{2} Curry shoots the ball twice. What is the probability that one shot makes it into the basket, and one shot does not?\vskip 0.1in

\begin{tabular}{l@{\hskip 1in}l@{\hskip 1in}l@{\hskip 1in}l}
{\bubble}\quad ${\displaystyle (0.58\times0.42)^2 }$
&\bubble \quad  ${\displaystyle 0.58 \times 0.42 }$ \\[10pt]
\solutionbubble \quad  ${\displaystyle (0.58\times0.42) + (0.42\times0.58)}$
&\bubble \quad ${\displaystyle 1 - (0.58)^2 }$
\end{tabular}
\end{enumerate}


\begin{enumerate}[resume]
\vskip .4in
Digging deeper into Steph Curry's basketball record, the students find that 80\% of Curry’s shots are contested - that is, someone is actively trying to block his shot or make him miss. When a shot is contested, Curry has a 55\% chance of successfully shooting the ball in the basket any time he tries. When his shots are not contested, Curry has a 70\% chance of shooting the ball in the basket. 



\vskip.4in
\subq{2} Given that Steph Curry's shot was uncontested, what is the probability the shot did not make it in the basket?\vskip 0.1in

\begin{tabular}{l@{\hskip 1in}l@{\hskip 1in}l@{\hskip 1in}l}
{\bubble}\quad ${\displaystyle \frac{0.2\times0.3 }{(0.2\times0.3 + 0.8\times0.45)}}$
&\bubble \quad  0.42 \\[12pt]
\solutionbubble \quad  0.30
&\bubble \quad ${\displaystyle (0.2\times0.3) + (0.8\times0.45) }$
\end{tabular}



\vskip .4in
\subq{2} Given that Steph Curry took three contested shots in a row, what is the probability that at least one of them went in?\vskip 0.1in

\begin{tabular}{l@{\hskip 1in}l@{\hskip 1in}l}
\solutionbubble \quad ${\displaystyle 1 - (0.45)^3}$
&\bubble \quad  ${\displaystyle 1 - (3\times0.45) }$ \\[10pt]
\bubble \quad  ${\displaystyle \frac{0.80\times0.55}{[(0.80\times0.55) + (0.20\times0.70)]^3}}$
&\bubble \quad ${\displaystyle 0.55^3 }$
\end{tabular}



\vskip .4in
\subq{2} Given that Steph Curry made the shot, what is the probability the shot was contested?\\

\begin{tabular}{l@{\hskip 1in}l@{\hskip 1in}l@{\hskip 1in}l}
{\bubble} \quad ${\displaystyle \frac{0.20\times0.70}{\big((0.80\times0.55) + (0.20\times 0.70)\big)}}$
&\bubble \quad  ${\displaystyle 1 - (0.45)^3}$\\[10pt]
\bubble \quad 0.8
&\solutionbubble \quad  ${\displaystyle \frac{0.80\times0.55}{\big((0.80\times0.55) + (0.20\times0.70)\big)}}$
\end{tabular}

\end{enumerate}

