%!TEX root = ../final.tex
\question A jar contains 100 jelly beans of four different colors - orange,
green, blue, and purple - in equal amounts. \textbf{In this question, if you
select the Other choice, you must state the correct expression in the space
provided.}

\begin{parts}
  \part[2] Suppose Sam only likes green jelly beans. He picks five beans at
  random without replacement from the jar. What is the chance he gets all green
  beans?

  \begin{multicols}{2}
  \begin{checkboxes}
    \correctchoice $ \frac{25}{100} \cdot \frac{24}{99} \cdot \frac{23}{98}
      \cdot \frac{22}{97} \cdot \frac{21}{96} $
    \choice $ \left( \frac{25}{100} \right)^5 $
    \choice $ \frac{25}{100} \cdot \frac{24}{100} \cdot \frac{23}{100} \cdot
      \frac{22}{100} \cdot \frac{21}{100} $
    \choice Other
  \end{checkboxes}
  \columnbreak
  If Other selected, write correct expression:
  \end{multicols}

  \part[3] Suppose he replaces the five previous beans and picks another five,
  this time with replacement. What is the chance he gets at least one green
  bean?

  \begin{multicols}{2}
  \begin{checkboxes}
    \choice $ 1 - \left( \frac{25}{100} \right)^5 $
    \choice $ 1 - \frac{25}{100} \cdot \frac{24}{100} \cdot \frac{23}{100}
      \cdot \frac{22}{100} \cdot \frac{21}{100} $
    \correctchoice $ 1 - \left(\frac{75}{100} \right)^5 $
    \choice Other
  \end{checkboxes}
  \columnbreak
  If Other selected, write correct expression:
  \end{multicols}

  \part[3] If Sam puts the beans back in the jar and then draws four beans
  without replacement, what is the chance that all four beans are different
  colors?

  \begin{multicols}{2}
  \begin{checkboxes}
    \choice $ \frac{25}{100} \cdot \frac{24}{99} \cdot \frac{23}{98} \cdot
      \frac{22}{97} $
    \choice $ 1 - \frac{25}{100} \cdot \frac{24}{99} \cdot \frac{23}{98} \cdot
      \frac{22}{97} $
    \choice $ \frac{25}{100} \cdot \frac{25}{99} \cdot \frac{25}{98} \cdot
      \frac{25}{97} $
    \correctchoice Other
  \end{checkboxes}
  \columnbreak
  If Other selected, write correct expression:
  \end{multicols}

  \begin{solution}

  \[ \frac{100}{100} \cdot \frac{75}{99} \cdot
     \frac{50}{98} \cdot \frac{25}{97} \]

  \end{solution}

  \part[4] Sam receives a gift jar of 400 jellybeans that has 50 orange, 50
  green, 150 blue, and 150 purple jellybeans. He's confused because he thinks
  the jar should have around the same proportion of each color, so he runs a
  hypothesis test.

  Null hypothesis: Each jellybean color has equal probability of
  appearing.

  Alternative: The jellybean colors appear with some other distribution.

  He selects the total variation distance as his test statistic.

  \begin{multicols}{2}
    Draw a rough sketch of the empirical distribution of the test statistic
    under the null hypothesis. You must:

    \begin{enumerate}
      \item Include the origin (0, 0) in your plot.
      \item Mark the observed value of the test statistic as a vertical line.
      \item Shade in the area corresponding to the P-value.
    \end{enumerate}

    Don't worry about x/y labels or whether you shaded in exactly the right
    amount of area.

    \columnbreak

    \begin{solutionorbox}[2in]
      TODO(sam): Add plot.
    \end{solutionorbox}
  \end{multicols}
\end{parts}
