\q{8}{You Studied for these Studies}

\begin{enumerate}

\subq{2} A medical observational study finds a high positive association between drinking coffee and having lung cancer in a group of individuals. Which of the following statements, if true, could present a confounding factor to the study? Choose the best answer.  
\begin{itemize}[label = \bubble]
\item There is a strong positive association between having lung cancer and drinking coffee in this group.
\item There is a strong positive association between drinking coffee and smoking in this group.
\item There is a no association between smoking and having lung cancer in this group.
\item All of the above
\item None of the above 
\end{itemize}
\solution{Option 2}

\subq{2} Researchers decide to test their new disease treatment equipment against their older equipment. However, their new disease equipment requires patients remain hydrated. Researchers select a group of 300 patients for this study; some of the participants will use the new equipment, while the others will use the old equipment. \\
\textbf{Mark all of the following options which} would help control for confounding factors in this study. 
\begin{itemize}[label = \bubble]
\item Requiring patients who are treated with the older equipment remain hydrated.
\item Requiring patients who are treated with the newer equipment remain dehydrated.
\item Assigning patients to groups at random.
\item Assigning different amounts of water randomly to individuals in both groups.
\item None of the above
\end{itemize}
\solution{Option 1 and 3}

\subq{4} A local store is the only umbrella store in a large radius. They decide to test whether or not the quality of their umbrellas impacts their yearly sales. In 2016, their umbrellas were of a very high quality and they sold 1,500 umbrellas. In 2017, their umbrellas were of average quality and they sold 1,000 umbrellas. \\ \\
The store is tempted to explain this phenomenon by claiming that a higher quality of umbrellas causes more sales. As data scientists, however, we are more hesitant to come to this conclusion. Give \textbf{two different specific} alternative explanations that could explain the results of the experiment above. You may \textbf{not} simply claim that this is an observational study. 
\\ \\
1. \\ \\ \\ \\ \\ \\ \\ \\
2. \\ \\ \\ \\ \\ \\ \\ \\
\solution{Two reasons include: \\
1. It didn't rain as much in 2017. No need to buy umbrellas \\
2. People who bought their umbrellas in 2016 didn't need a new one for 2017, so they didn't buy again in 2017. \\
Many options were accepted, if they didn't mention observational study and were specific.}
\end{enumerate}



