\q{10}{Spotify Shuffle}

Fahad creates a Spotify music playlist by randomly sampling 100 songs from a large collection of tunes from the Data 8 staff music library. It is known that staff library contains 20\% Hip-Hop songs, 35\% Pop songs, 15\% Rock songs, 25\% Dance songs, and 5\% Country songs. 

Vinitra notices that in Fahad's playlist, there are 30\% Hip-Hop songs, 30\% Pop songs, 20\% Rock songs, 18\% Dance songs, and 2\% Country songs. 

Initially, Vinitra believes that Fahad's claim that he randomly sampled 100 songs from the large staff library is false. Specifically, she believes he purposefully sampled more Hip-Hop songs. 
\begin{enumerate}
\subq{3} Describe a test statistic that we could compute given a sample that can help us pick between the two viewpoints: Fahad sampled the songs randomly and any difference is due to chance, or he was biased in his sampling technique and sampled more Hip-Hop songs. \\ \\ \\ \\ 
\solution{The percentage of songs that are Hip-Hop or the difference between actual number of hip hop songs and expected number of hip hop songs. TVD does not work because we specifically care if Hip Hop was higher than expected, not the whole distribution. Moreover, absolute value was incorrect because we care about a direction. }

\subq{2} Fill in the blank with the best number possible. No need to show your work. \\
If the null hypothesis was true, we expect our test statistic to be roughly equal to \underline{\hspace{3cm}}, and any difference in our sample is just due to random chance. \\ \\
\solution{20\% if your answer is percentage of hip hop songs above, or 0 otherwise. Your answer here depends on what you wrote on part a and was graded accordingly.} \\
Now, Vinitra decides that she does not care about Fahad's bias towards Hip-Hop. Instead, she simply does not believe that Fahad truly created his playlist by randomly sampling the 100 songs from the large staff library. She does not know how he sampled, but she believes it is not completely random. \\ 

\subq{3} Describe a test statistic that can help pick between the two viewpoints: Fahad sampled the songs randomly and any difference is due to chance, or he did not sample the songs randomly from the staff playlist.   \\ \\ \\ \\ 
\solution{The TVD between Fahad's claimed distribution of music genres and the sample that we obtain.}
\subq{2} Fill in the blank with the best number possible. No need to show your work. \\
If the null hypothesis was true, we expect our test statistic to be roughly equal to \underline{\hspace{3cm}}, and any difference in our sample is just due to random chance. \\ \\
\solution{0}
\end{enumerate}